---
title: "Software"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval=FALSE)
```

# R packages

### [assert](https://github.com/OlivierBinette/assert)

<!--[![CRAN\_Status\_Badge](https://www.r-pkg.org/badges/version/assert)](https://cran.r-project.org/package=assert) -->

Lightweight validation tool for checking function arguments and data analysis scripts.

```{r}
install.packages("assert")
```


### [dgaFast](https://github.com/OlivierBinette/dgaFast)

Multiple Systems Estimation Using Decomposable Graphical Models. This is an efficient re-implementation and extension of the `dga` R package.

```{r}
devtools::install_github("OlivierBinette/dgaFast")
```


# Javascript apps

### [Fractals](https://olivierbinette.github.io/Fractals/)

High resolution visualization for the Mandelbrot set. A [Java version](https://github.com/olivierBinette/Fractals) with more features is also available.

### [Earthquakes](https://olivierbinette.github.io/earthquakes/)

Visualize earthquakes on the globe.

# Other software

- **[splinit](https://github.com/OlivierBinette/splinit)**: Closed curve reconstruction in R using the fused lasso and minimal hamiltonian cycles.

- **[lipsample](https://github.com/OlivierBinette/lipsample)**: Sampling from arbitrary Lipschitz continuous densities on the interval in matlab.

- **[prettyplot](https://github.com/OlivierBinette/prettyplot)**: Prettier base plots in R.
