---
title: "Software"
---
 
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval=FALSE)
```

# Python packages

### [ER-Evaluation](https://github.com/OlivierBinette/ER-Evaluation)

An End-to-End Evaluation Framework for Entity Resolution Systems.

```{bash, eval=FALSE}
pip install er-evaluation
```


### [PatentsView-Evaluation](https://github.com/PatentsView/PatentsView-Evaluation/)

**pv_evaluation** is a Python package for the evaluation and benchmarking of [PatentsView](https://patentsview.org/) disambiguation algorithms. It provides summary statistics, performance evaluation metrics, and representative performance estimators. See the [project website](https://patentsview.github.io/PatentsView-Evaluation/build/html/index.html) for the full documentation.

```{bash, eval=FALSE}
pip install pv-evaluation
```

### [StringCompare](https://github.com/olivierbinette/StringCompare)

**StringCompare** is a Python package (implemented in C++ through pybind11) for efficient string similarity computation and approximate string matching.

```{bash, eval=FALSE}
pip install git+https://github.com/OlivierBinette/stringcompare.git
```


### 🚧 [GroupByRule](https://github.com/olivierbinette/groupbyrule)

Deduplicate data using fuzzy and deterministic matching rules. This is under construction.

```{bash, eval=FALSE}
pip install git+https://github.com/OlivierBinette/groupbyrule.git
```


# R packages

### [FingermatchR](https://github.com/forensic-science/fingermatchR)

Fingerprint matching tools based on NIST's Biometric Image Software, on FingerJet minutiae extraction tool, and on the libfmr library.

```{r}
devtools::install_github("forensic-science/fingermatchR")
```

### [MSETools](https://github.com/OlivierBinette/MSETools)

Code and analyses for the paper titled “On the Reliability of Multiple Systems Estimation for the Quantification of Modern Slavery” (Binette and Steorts, 2021).

```{r}
devtools::install_github("OlivierBinette/MSETools")
```

### [cache](https://github.com/OlivierBinette/cache)

[![CRAN\_Status\_Badge](https://www.r-pkg.org/badges/version/assert)](https://cran.r-project.org/package=cache)

Simple interface to caching which works across interactive R sessions, R scripts and Rmarkdown documents.

```{r}
install.packages("cache")
```

### [assert](https://github.com/OlivierBinette/assert)

[![CRAN\_Status\_Badge](https://www.r-pkg.org/badges/version/assert)](https://cran.r-project.org/package=assert)

Lightweight validation tool for checking function arguments and data analysis scripts.

```{r}
install.packages("assert")
```

### [dgaFast](https://github.com/OlivierBinette/dgaFast)

Multiple Systems Estimation Using Decomposable Graphical Models. This is an efficient re-implementation and extension of the [**dga**](https://github.com/hrdag/dga) R package (it is now part of [**dga**](https://github.com/hrdag/dga)).

```{r}
devtools::install_github("OlivierBinette/dgaFast")
```


### [TessTools](https://github.com/OlivierBinette/TessTools)

Tools for the use of Tesseract OCR in R and for the analysis of historical newspaper archives.

```{r}
devtools::install_github("OlivierBinette/TessTools")
```


### [splinit](https://github.com/OlivierBinette/splinit)

Periodic spline regression and closed curve reconstruction.

```{r}
devtools::install_github("OlivierBinette/splinit")
```

### [pretty](https://github.com/OlivierBinette/pretty)

Better baser plots in R.

```{r}
devtools::install_github("OlivierBinette/pretty")
```

# Javascript apps

### [Fractals](https://olivierbinette.github.io/Fractals/)

High resolution visualization for the Mandelbrot set. A [Java version](https://github.com/olivierBinette/Fractals) with more features is also available.

### [Earthquakes](https://olivierbinette.github.io/earthquakes/)

Visualize earthquakes on the globe.

# Other software

- **[lipsample](https://github.com/OlivierBinette/lipsample)**: Sampling from arbitrary Lipschitz continuous densities on the interval in matlab.
